Self-assembly of colloid-cholesteric composites: A route to switchable optical materials

### 2013-11-08 papers/2012-sandwich/CholColloids.tex
Updated text main paper and supplement
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@2235 40876441-3496-0410-a613-a2fca35b2ae2

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{text-fig3.jpg}}
\caption{Snapshots of the steady states obtained when a dispersion of colloids is inserted into a thermodynamically stable bulk-BPIII (A), and finally subjected to an electric field along the vertical direction (B). The electric field leads to the formation of a honeycomb structure with hexagonal ordering perpendicular to the field direction. 
Structures correspond to $w=0.23$ and $\phi=5\%$ (see Supporting Information
for full list of parameters). }
\end{figure}

>>>>

\begin{figure}
\centerline{
\includegraphics[width=0.35\textwidth]{col_disc_x_run1267.png}
\begin{minipage}[t]{0.17\textwidth}
\vspace*{-4.6cm}
\includegraphics[width=\textwidth]{sq_x_run1267.png}
\includegraphics[width=\textwidth]{sq_y_run1267.png}
\end{minipage}
\includegraphics[width=0.35\textwidth]{col_disc_x_run1341.png}
\begin{minipage}[t]{0.17\textwidth}
\vspace*{-4.6cm}
\includegraphics[width=\textwidth]{sq_x_run1341.png}
\includegraphics[width=\textwidth]{sq_y_run1341.png}
\end{minipage}
}
\caption{Snapshots of the steady states obtained when a dispersion of colloids is inserted into a thermodynamically stable bulk-BPIII (A). The isotropic nature of the state is refected in structure factor data (B and C for a cut through the 3D structure factor at $k_x=0$ and $k_y=0$, respectively). Subjected to an electric field along the x-direction a honeycomb structure forms with hexagonal ordering perpendicular to the field direction (D). The hexagonal structure is also evident from structure factor data (E and F for cuts at $k_x=0$ and $k_y=0$, respectively).     
Structures correspond to $w=0.23$ and $\phi=5\%$ (see Supporting Information
for full list of parameters). }
\end{figure}

### 2013-11-08 papers/2012-sandwich/support.tex
Updated text main paper and supplement
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@2235 40876441-3496-0410-a613-a2fca35b2ae2

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.95\columnwidth]{support-fig7.pdf}
\end{center}
\caption{Panels A and B as for Fig. 3, but with the disclination lines
removed for clarity. Panel C shows the situation when the field is
switched off: a residual anisotropic structure remains which reflects the
structure induced by the electric field. The electric field direction
when switched on (panel B) is into the plane of the paper.}
\end{figure}

%\newpage

>>>>

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1341.png}
\includegraphics[width=0.32\columnwidth]{col_parallel_y_run1342.png}
\includegraphics[width=0.32\columnwidth]{col_parallel_z_run1342.png}\\
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1342.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1342.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1342.png}
\end{center}
\caption{Particle distribution and cuts through the structure factor: Panel A shows state D of Fig.3 with field along x in parallel projection. The disclinations are not plotted for clarity. The distribution after switch-off is shown in panel D (along the former field direction x, and with the view along y and z, respectively. Panels E and F are cuts though the 3D structure factor of state (D/B/C) at $k_x=0$ and $k_y=0$. The structure factor data is for wave vectors $k{x,y,z} \in [-3\pi/8 , 3\pi/8]$.}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.32\columnwidth]{col_parallel_y_run1343.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1343.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1343.png}\\
\includegraphics[width=0.32\columnwidth]{col_parallel_y_run1344.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1344.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1344.png}\\
\end{center}
\caption{Particle distribution in parallel projection and cuts through the structure factor: Panel A shows the distribution while the field along y is on after a run with the field along x (SI Fig.7). Cuts through the corresponding structure factor at $k_x=0$ and $k_y=0$ are shown in panel B and C. The situation after switch-off is depicted in panel D (panels E and F for cuts through the structure factor at $k_x=0$ and $k_y=0$). The structure factor data is for wave vectors $k{x,y,z} \in [-3\pi/8 , 3\pi/8]$.}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1345.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1345.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1345.png}\\
\includegraphics[width=0.32\columnwidth]{col_parallel_x_run1347.png}
\includegraphics[width=0.32\columnwidth]{sq_x_run1347.png}
\includegraphics[width=0.32\columnwidth]{sq_y_run1347.png}
\end{center}
\caption{Particle distribution in parallel projection and cuts through the structure factor: Panel A shows the distribution while the field along x is on after a run with the field along y (SI Fig.8). Cuts through the corresponding structure factor at $k_x=0$ and $k_y=0$ are shown in panel B and C. The situation after switch-off is depicted in panel D (panels E and F for cuts through the structure factor at $k_x=0$ and $k_y=0$). The structure factor data is for wave vectors $k{x,y,z} \in [-3\pi/8 , 3\pi/8]$.}
\end{figure}

%\newpage
\clearpage
